### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Change to bib

A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
state-to-state rate in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev:104906}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
the Marcus rate equation in the semiclassical limit.  The model itself is parameterized by the
vibrational normal mode frequencies, the electronic energies, and energy derivatives
at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
The approach has been intensively used and testified by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura:107402,tamura:021103,singh:194905,Bittner:2014aa}.
Central to our work here is the use of a mode-projection scheme
 % which is similar to the Page-rank algorithm used by internet search engines such as
 % Google and Netflix\cite{brin1998anatomy, page2004method},
 which parses out a
reduced set of nuclear motions primarily coupled to the quantum transition.
We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.

Using the TCLME approach,  we recently investigated
triplet-triplet excitation energy transfer between a naphthalene donor and a
benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{xunmo2014}
\begin{figure}
%\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
\includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
\caption{Molecular structure of naphthalene donor and a
benzaldehyde acceptor linked by various bridging units. }\label{struct}
\end{figure}
Such systems were the basis of a  classic series of experiments by
Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
which verified the existence of the Marcus inverted regime.
In Ref. \cite{xunmo2014} we showed that both
the autocorrelation function of the electronic coupling operators
and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
excellent approximation to the exact correlation functions and rate
constants computed using all normal modes, as well as to the experimental
and recent theoretical values for the transfer rates.\cite{subotnik2010predicting}

@@

% \subsection{Construction and parameterization}
Our method was detailed in Ref.\cite{xunmo2014} but to be self-contained, we briefly present it here.

@@

% We now separate Eq. ~\ref{ham1} into diagonal and
% off-diagonal terms
% \begin{eqnarray}
% \hat  H = \hat H_{o} + \hat V
% \end{eqnarray}
% and perform a polaron transform
% using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
% \begin{eqnarray}
% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
% n|(a^{\dagger}_i-a_i)}
%  \nonumber \\
% &=&
% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
% \label{unitary}
% \end{eqnarray}
% under which the transformed Hamiltonian is written in terms of the
% diagonal elements
% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
% =\sum_n\tilde\epsilon_n |n\rangle \langle
% n|+\sum_i\omega_ia^{\dagger}_ia_i,
%  \end{eqnarray}
% with  the renormalized electronic energies,
% \begin{eqnarray}
% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
% \end{eqnarray}
% and off-diagonal terms,
% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
% \label{opm}
% \end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
% %C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
% C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
% $$
% is the autocorrelation function of the
% polaron-transformed electron-phonon coupling operator in the Heisenberg representation and
% $\langle \cdots \rangle$ denotes a thermal average over the
% vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev:104906}.
% Using this approach , the golden-rule rates are given by
% \begin{eqnarray}
% k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
% \label{gr-expression}
% \end{eqnarray}
% In a practical sense, we take $\tau$ to be some finite time at which the
% autocorrelation function $C(t)$
% has relaxed to zero.

% Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
% the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
% For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
% In our previous work we showed that both $C(t)$
% and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
% excellent agreement with the exact quantities computed using  the full set of
% normal modes, as well as the experimental rates,
% when parameterized using accurate quantum chemical data.\cite{xunmo2014}

@@

Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev:104906}. The derivation is lengthy so we present it briefly.

\subsection{Transition Rate and Autocorrelation}
We start from a more general Hamiltonian:
\begin{eqnarray}
H=\left(\begin{array}{cc}
\epsilon_{1} & 0\\
0 & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
\nonumber \\
\label{ham1}
\end{eqnarray}
then perform a polaron transform
using the unitary transformation~\cite{grover:2099,rice:2504,pereverzev:104906}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
%C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
After lengthy derivation we get the autocorrelation function in the Heisenberg representation
$$
C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
$$
where $\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev:104906}.
Using this approach , the golden-rule rates are given by
\begin{eqnarray}
k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}
In a practical sense, we take $\tau$ to be some finite time at which the
autocorrelation function $C(t)$
has relaxed to zero.

Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
In our previous work we showed that both $C(t)$
and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
excellent agreement with the exact quantities computed using  the full set of
normal modes, as well as the experimental rates,
when parameterized using accurate quantum chemical data.\cite{xunmo2014}

@@

% The linear coupling parameter $ {\mathbf g}_{22}$ defines
% a force
% along a vector connecting the
% the initial and final equilibrium geometries of the molecule.
% This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
% using the ER localization
% scheme to approximate the donor and acceptor states.
% By analyzing this force we can gain the insight into the dynamics of the transition as well as
% open an avenue for developing improved approximations for transition rates.
% In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
% out a series of nuclear displacements that are most important for
% the transition.   We refer to the highest-ranked mode identified by the algorithm
% as the ``primary Lanczos mode'' (PLM).

@@

\subsection{Constructing Primary Lanczos Modes}
The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam} defines
a force
along a vector connecting
the initial and final equilibrium geometries of the molecule.
This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
using the ER localization
scheme to approximate the donor and acceptor states.
By analyzing this force we can gain the insight into the dynamics of the transition as well as
open an avenue for developing improved approximations for transition rates.
In our previous work \cite{xunmo2014},  we presented a Lanczos-base ranking algorithm that project
out a series of nuclear displacements that are most important for
the transition.   We refer to the highest-ranked mode identified by the algorithm
as the ``primary Lanczos mode'' (PLM).
The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
At each step indexed by $k$,  we define a projection operator
\begin{eqnarray}
{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
\end{eqnarray}
and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
We also construct
\begin{eqnarray}
\mathbf p = \sum_{k} \mathbf P_{k}
\end{eqnarray}
as  the total projection operator for all ${k} \le N$ modes.
We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
\begin{eqnarray}
\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
\end{eqnarray}
and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
The first set of these  will have a single
non-trivial eigenvalue and the second set
will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
to form the orthogonal transformation matrix
\begin{eqnarray}
{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
\end{eqnarray}
and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
 At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
a diagonal submatrix in the lower-right.

@@

However, as seen on our previous work \cite{xunmo2014},
the approximate correlation function does not need to give perfect agreement
with the exact correlation function to produce an accurate transition rate constant (Eq. 4).
To assess the accuracy of using different combinations of local modes,
we calculate the transition rate constants for various combinations up to 10 modes on
each moiety and compare to the exact rate.
This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
naphthalene produces an agreement with the exact result to within 5\%.
For the d26ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
naphthalene is simply a larger molecule with more normal modes.

@@

@@

\begin{thebibliography}{16}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Marcus}(1956)}]{marcus1956theory}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
  {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
  {pages} {966} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Marcus}(1965)}]{marcus1965theory}%
  \BibitemOpen

>>>>

A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
state-to-state rate in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
the Marcus rate equation in the semiclassical limit.  The model itself is parameterized by the
vibrational normal mode frequencies, the electronic energies, and energy derivatives
at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
The approach has been intensively used and testified by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
Central to our work here is the use of a mode-projection scheme
 % which is similar to the Page-rank algorithm used by internet search engines such as
 % Google and Netflix\cite{brin1998anatomy, page2004method},
 which parses out a
reduced set of nuclear motions primarily coupled to the quantum transition.
We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.

Using the TCLME approach,  we recently investigated
triplet-triplet excitation energy transfer between a naphthalene donor and a
benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
\begin{figure}
%\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
\includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
\caption{Molecular structure of naphthalene donor and a
benzaldehyde acceptor linked by various bridging units. }\label{struct}
\end{figure}
Such systems were the basis of a  classic series of experiments by
Closs and Miller\cite{miller1984intramolecular,closs1988determination,closs1989connection}
which verified the existence of the Marcus inverted regime.
In Ref. \cite{yang2014intramolecular} we showed that both
the autocorrelation function of the electronic coupling operators
and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
excellent approximation to the exact correlation functions and rate
constants computed using all normal modes, as well as to the experimental
and recent theoretical values for the transfer rates.\cite{subotnik2010predicting}

@@

% \subsection{Construction and parameterization}
Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.

@@

% We now separate Eq. ~\ref{ham1} into diagonal and
% off-diagonal terms
% \begin{eqnarray}
% \hat  H = \hat H_{o} + \hat V
% \end{eqnarray}
% and perform a polaron transform
% using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
% \begin{eqnarray}
% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
% n|(a^{\dagger}_i-a_i)}
%  \nonumber \\
% &=&
% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
% \label{unitary}
% \end{eqnarray}
% under which the transformed Hamiltonian is written in terms of the
% diagonal elements
% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
% =\sum_n\tilde\epsilon_n |n\rangle \langle
% n|+\sum_i\omega_ia^{\dagger}_ia_i,
%  \end{eqnarray}
% with  the renormalized electronic energies,
% \begin{eqnarray}
% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
% \end{eqnarray}
% and off-diagonal terms,
% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
% \label{opm}
% \end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
% %C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
% C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
% $$
% is the autocorrelation function of the
% polaron-transformed electron-phonon coupling operator in the Heisenberg representation and
% $\langle \cdots \rangle$ denotes a thermal average over the
% vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev2006time}.
% Using this approach , the golden-rule rates are given by
% \begin{eqnarray}
% k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
% \label{gr-expression}
% \end{eqnarray}
% In a practical sense, we take $\tau$ to be some finite time at which the
% autocorrelation function $C(t)$
% has relaxed to zero.

% Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
% the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
% For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
% In our previous work we showed that both $C(t)$
% and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
% excellent agreement with the exact quantities computed using  the full set of
% normal modes, as well as the experimental rates,
% when parameterized using accurate quantum chemical data.\cite{yang2014intramolecular}

@@

Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}. The derivation is lengthy so we present it briefly.

\subsection{Transition Rate and Autocorrelation}
We start from a more general Hamiltonian:
\begin{eqnarray}
H=\left(\begin{array}{cc}
\epsilon_{1} & 0\\
0 & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
\nonumber \\
\label{ham1}
\end{eqnarray}
then perform a polaron transform
using the unitary transformation~\cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
\label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
\label{opm}
\end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
%C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
After lengthy derivation we get the autocorrelation function in the Heisenberg representation
$$
C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
$$
where $\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev2006time}.
Using this approach , the golden-rule rates are given by
\begin{eqnarray}
k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
\label{gr-expression}
\end{eqnarray}
In a practical sense, we take $\tau$ to be some finite time at which the
autocorrelation function $C(t)$
has relaxed to zero.

Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
In our previous work we showed that both $C(t)$
and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
excellent agreement with the exact quantities computed using  the full set of
normal modes, as well as the experimental rates,
when parameterized using accurate quantum chemical data.\cite{yang2014intramolecular}

@@

% The linear coupling parameter $ {\mathbf g}_{22}$ defines
% a force
% along a vector connecting the
% the initial and final equilibrium geometries of the molecule.
% This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
% using the ER localization
% scheme to approximate the donor and acceptor states.
% By analyzing this force we can gain the insight into the dynamics of the transition as well as
% open an avenue for developing improved approximations for transition rates.
% In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
% out a series of nuclear displacements that are most important for
% the transition.   We refer to the highest-ranked mode identified by the algorithm
% as the ``primary Lanczos mode'' (PLM).

@@

\subsection{Constructing Primary Lanczos Modes}
The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam} defines
a force
along a vector connecting
the initial and final equilibrium geometries of the molecule.
This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
using the ER localization
scheme to approximate the donor and acceptor states.
By analyzing this force we can gain the insight into the dynamics of the transition as well as
open an avenue for developing improved approximations for transition rates.
In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
out a series of nuclear displacements that are most important for
the transition.   We refer to the highest-ranked mode identified by the algorithm
as the ``primary Lanczos mode'' (PLM).
The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
At each step indexed by $k$,  we define a projection operator
\begin{eqnarray}
{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
\end{eqnarray}
and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
We also construct
\begin{eqnarray}
\mathbf p = \sum_{k} \mathbf P_{k}
\end{eqnarray}
as  the total projection operator for all ${k} \le N$ modes.
We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
\begin{eqnarray}
\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
\end{eqnarray}
and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
The first set of these  will have a single
non-trivial eigenvalue and the second set
will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
to form the orthogonal transformation matrix
\begin{eqnarray}
{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
\end{eqnarray}
and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
 At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
a diagonal submatrix in the lower-right.

@@

However, as seen on our previous work \cite{yang2014intramolecular},
the approximate correlation function does not need to give perfect agreement
with the exact correlation function to produce an accurate transition rate constant (Eq. 4).
To assess the accuracy of using different combinations of local modes,
we calculate the transition rate constants for various combinations up to 10 modes on
each moiety and compare to the exact rate.
This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
naphthalene produces an agreement with the exact result to within 5\%.
For the d26ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
naphthalene is simply a larger molecule with more normal modes.

@@

% \bibliography{Dbib}

@@

% \begin{thebibliography}{16}%
% \makeatletter
% \providecommand \@ifxundefined [1]{%
%  \@ifx{#1\undefined}
% }%
% \providecommand \@ifnum [1]{%
%  \ifnum #1\expandafter \@firstoftwo
%  \else \expandafter \@secondoftwo
%  \fi
% }%
% \providecommand \@ifx [1]{%
%  \ifx #1\expandafter \@firstoftwo
%  \else \expandafter \@secondoftwo
%  \fi
% }%
% \providecommand \natexlab [1]{#1}%
% \providecommand \enquote  [1]{``#1''}%
% \providecommand \bibnamefont  [1]{#1}%
% \providecommand \bibfnamefont [1]{#1}%
% \providecommand \citenamefont [1]{#1}%
% \providecommand \href@noop [0]{\@secondoftwo}%
% \providecommand \href [0]{\begingroup \@sanitize@url \@href}%
% \providecommand \@href[1]{\@@startlink{#1}\@@href}%
% \providecommand \@@href[1]{\endgroup#1\@@endlink}%
% \providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
%   `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
% \providecommand \@@startlink[1]{}%
% \providecommand \@@endlink[0]{}%
% \providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
% \providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
% \providecommand \urlprefix  [0]{URL }%
% \providecommand \Eprint [0]{\href }%
% \providecommand \doibase [0]{http://dx.doi.org/}%
% \providecommand \selectlanguage [0]{\@gobble}%
% \providecommand \bibinfo  [0]{\@secondoftwo}%
% \providecommand \bibfield  [0]{\@secondoftwo}%
% \providecommand \translation [1]{[#1]}%
% \providecommand \BibitemOpen [0]{}%
% \providecommand \bibitemStop [0]{}%
% \providecommand \bibitemNoStop [0]{.\EOS\space}%
% \providecommand \EOS [0]{\spacefactor3000\relax}%
% \providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
% \let\auto@bib@innerbib\@empty
% %</preamble>
% \bibitem [{\citenamefont {Marcus}(1956)}]{marcus1956theory}%
%   \BibitemOpen
%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
%   {Marcus}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The
%   Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
%   {pages} {966} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
